Matching bullets

### 2015-11-23 imaging-paper.Rnw
cross-correlation added

subLOF <- rbind(data.frame(subLOF1), data.frame(subLOF2))
subLOF1$y <- subLOF1$y + 19*1.5625 # working now!!!
subLOF <- rbind(data.frame(subLOF1), data.frame(subLOF2))

@@

@@

lines <- matches %>% group_by(lineid) %>% summarise(
  meany = mean(y, na.rm=T),
  miny = min(y, na.rm=T),
  maxy = max(y, na.rm=T) + 1.5625,
  match = isMatch(lineid, type),
  type = type1[1]
)
lines <- subset(lines, lineid != 0)
@
\begin{figure}
\centering
    \subfloat[Crosscuts at $x = 100$.\label{fig:crosscut}]{%
<<crosscuts, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3, out.width='.49\\textwidth'>>=
qplot(y, resid, group=bullet, colour=bullet, data=lof, 
      geom="line", alpha=I(0.6)) + 
  scale_colour_brewer("", palette="Set1") + theme_bw() +
  theme(legend.position = c(.9, .2))
@
    }
    \hfill
    \subfloat[Adjusted (Bullet 1-5 horizontally shifted) crosscuts at $x = 100$.\label{fig:crosscutX}]{%
<<crosscutsX, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3, out.width='.49\\textwidth'>>=
qplot(y, resid, group=bullet, colour=bullet, data=lofX, 
      geom="line", alpha=I(0.6)) + 
  scale_colour_brewer(palette="Set1") + theme_bw() +
  theme(legend.position="none")
@
    }
\caption{\label{fig:cross100} Lines showing surface crosscuts at $x = 100$. A horizontal shift of the values of Bullet 1-5 to the right shows the similarity of the striation marks.}
\end{figure}

\hh{Using (for now) a single crosscut across the surface, we extract the values and remove the class characteristics using a loess fit as before. This enables us to focus on the individual characterists. Striation marks show up in this representations as peaks and valleys. Figure~\ref{fig:cross100} shows lines of the surface crosscut at $x = 100$. A horizontal shift of one of the lines (result shown in (b)) emphasizes the strong similarities.}

@@

\hh{Figure~\ref{fig:match} gives an overview of the automated matching routine: after smoothing the scan with a loess of a very small span, shown in (a), we define a striation mark as a groove or a peak if it exceeds a pre-set threshold (of 0.75$\mu m$; obviously this is a crucial parameter. For more discussion see Figure~\ref{fig:thresholds}). Two lines are defined as a match, if their peak/groove base at the threshold overlaps. If there is no overlap, a peak/groove leads to a mismatch. We then count the number of maximum consecutive matches. In this example, the number of consecutive matching striations (CMS) is fifteen, a very high number indicative of a match between the bullets. For lead bullets, such as this, Biasotti \cite{biasotti:1959} XXX need more references XXX considered four or more consecutive lines to be sufficient evidence of a match. }

>>>>

#subLOF <- rbind(data.frame(subLOF1), data.frame(subLOF2))
subLOF1$y <- subLOF1$y + 19*1.5625 # working now!!!
subLOF <- rbind(data.frame(subLOF1), data.frame(subLOF2))

@@

<<twolands100adjust, echo=FALSE>>=
images <- file.path(datadir, dir(datadir))

subLOFx1 <- subset(lof, bullet=="Br1 Bullet 1-5")
subLOFx2 <- subset(lof, bullet=="Br1 Bullet 2-1")
subLOFx1$y <- subLOFx1$y - min(subLOFx1$y)
subLOFx2$y <- subLOFx2$y - min(subLOFx2$y)
ccf <- ccf(subLOFx1$resid, subLOFx2$resid, lag.max=100, plot=FALSE)
lag <- ccf$lag[which.max(ccf$acf)]
subLOFx1$y <- subLOFx1$y - lag*1.5625 
lofY <- rbind(data.frame(subLOFx1), data.frame(subLOFx2))

@@

lines <- matches %>% group_by(lineid) %>% summarise(
  meany = mean(y, na.rm=T),
  miny = min(y, na.rm=T),
  maxy = max(y, na.rm=T) + 1.5625,
  match = isMatch(lineid, type),
  type = type1[1]
)
lines <- subset(lines, lineid != 0)
@
\begin{figure}
\centering
    \subfloat[Crosscuts at $x = 100$.\label{fig:crosscut}]{%
<<crosscuts, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3, out.width='.49\\textwidth'>>=
qplot(y, resid, group=bullet, colour=bullet, data=lof, 
      geom="line", alpha=I(0.6)) + 
  scale_colour_brewer("", palette="Set1") + theme_bw() +
  theme(legend.position = c(.9, .2))
@
    }
    \hfill
    \subfloat[Adjusted (Bullet 1-5 horizontally shifted) crosscuts at $x = 100$.\label{fig:crosscutX}]{%
<<crosscutsX, echo=FALSE, dependson='twolands100', fig.width=7, fig.height=3, out.width='.49\\textwidth'>>=
# qplot(y, resid, group=bullet, colour=bullet, data=lofX, 
#       geom="line", alpha=I(0.6)) + 
#   scale_colour_brewer(palette="Set1") + theme_bw() +
#   theme(legend.position="none")
qplot(y, resid, group=bullet, colour=bullet, data=lofY, 
      geom="line", alpha=I(0.6)) + 
  scale_colour_brewer(palette="Set1") + theme_bw() +
  theme(legend.position="none")
@
    }
\caption{\label{fig:cross100} Lines showing surface crosscuts at $x = 100$. A horizontal shift of the values of Bullet 1-5 to the right shows the similarity of the striation marks.}
\end{figure}

Using (for now) a single crosscut across the surface, we extract the values and remove the class characteristics using a loess fit as before. This enables us to focus on the individual characterists. Striation marks show up in this representations as peaks and valleys. Figure~\ref{fig:cross100} shows lines of the surface crosscut at $x = 100$. A horizontal shift of one of the lines (result shown in (b)) emphasizes the strong similarities.
\hh{This horizontal shift is based on the cross-correlation between the two surface crosscuts. Let $f(t)$ and $g(t)$ define the values of the crosscut at $t$, then the cross-correlation between $f$ and $g$ at lag $k$ is defined as
\[
(f * g) (k) = \sum_t f(t+k) g(t),
\]
with suitable defined limits of the summation. 
}
\begin{figure}
<<ccf, echo=FALSE, fig.width = 7, fig.height = 3, out.width = '\\linewidth'>>=
lag <- ccf$lag[which.max(ccf$acf)]
qplot(x=ccf$lag, xend=ccf$lag, y = 0, yend= ccf$acf, geom="segment", colour = I("grey50")) + 
  theme_bw() + ylab("Correlation") + xlab("Lag k") +
  geom_segment(aes(x = lag, xend = lag, y = 0, yend =  max(ccf$acf)), colour="black") + 
  scale_x_continuous(breaks = c(-100, -50, lag, 0, 50, 100))
@
\caption{\label{fig:ccf}Cross-correlation between the two crosscuts shown in Figure~\ref{fig:crosscut} at lags between -100 and 100. At a lag of -10 the correlation peaks, indicating the largest amount of agreement between the crosscuts. Figure~\ref{fig:crosscutX} shows the lag-shifted crosscuts.}
\end{figure}

@@

\hh{Figure~\ref{fig:match} gives an overview of the rest of the automated matching routine: after smoothing the scan with a loess of a very small span, shown in (a), we define a striation mark as a groove or a peak if it exceeds a pre-set threshold (of 0.75$\mu m$; obviously this is a crucial parameter. For more discussion see Figure~\ref{fig:thresholds}). Two lines are defined as a match, if their peak/groove base at the threshold overlaps. If there is no overlap, a peak/groove leads to a mismatch. We then count the number of maximum consecutive matches. In this example, the number of consecutive matching striations (CMS) is fifteen, a very high number indicative of a match between the bullets. For lead bullets, such as this, Biasotti \cite{biasotti:1959} XXX need more references XXX considered four or more consecutive lines to be sufficient evidence of a match. }
